\begin{thebibliography}{99}

\bibitem{SiPM based photon counting detector for scanning digital radiography}
E.A. Babichev et al., SiPM based photon counting detector for scanning digital radiography, JINST 10 (2015) C03002

\bibitem{Silicon Photomultiplier's Gain Stabilization}
P. Dorosz et al., Silicon Photomultiplier's Gain Stabilization by Bias Correction for Compensation of the Temperature Fluctuations, , Nucl. Instrum. Meth. A 718 (2013) pp. 202–204

\bibitem{Temperature and Bias Voltage Dependence}
N. Dinu et al., Temperature and Bias Voltage Dependence of the MPPC Detectors, IEEE Oct. 30 2010-Nov. 6 2010 pp.215 - 219 

\bibitem{Characterization of SiPM: temperature dependencies}
Marco Ramilli, Characterization of SiPM: temperature dependencies, IEEE 19-25 Oct. 2008 pp. 2467 - 2470

\bibitem{Characterisation of a silicon photomultiplier device}
P.K. Lightfoot et al., Characterisation of a silicon photomultiplier device for applications in liquid argon based neutrino physics and dark matter searches, JINST 3 (2008) P10001

\bibitem{Characterisation Studies of Silicon Photomultipliers}
Patrick Eckert et al., Characterisation Studies of Silicon Photomultipliers, Nucl. Instrum. Meth. A 620 (2010) pp. 217–226 

\bibitem{Modeling crosstalk in silicon photomultipliers}
L. Gallego et al., Modeling crosstalk in silicon photomultipliers, Nucl. Instrum. Meth. A 787 (2015) pp. 153–156

\bibitem{Characterization and Simulation of the Response}
A. Vacheretc et al., Characterization and Simulation of the Response of Multi Pixel Photon Counters to Low Light Levels, Nucl. Instrum. Meth. A 656 (2011) pp. 69-83

\bibitem{After-pulsingandcross-talkinmulti-pixelphotoncounters}
Y. Du et al., After-pulsing and cross-talk in multi-pixel photon counters, Nucl. Instr. and Meth. A 596 (2008) pp. 396-401

\bibitem{Using MPPCs for T2K Fine Grain Detector}
Fabrice Retiere, Using MPPCs for T2K Fine Grain Detector, PoS PD07 (2006) 017


\bibitem{Modeling crosstalk and afterpulsing in siliconphoto multipliers}
J. Rosado et al., Modeling crosstalk and afterpulsing in silicon photomultipliers, Nucl. Instr. and Meth. A 787 (2015) pp. 153–156

\bibitem{Measurement of PDE of MPPC with different wavelengths of light}
Daniel Orme et al., Measurement of PDE of MPPC with different wavelengths of light, PoS PD09 (2009) 019


\end{thebibliography}

